Supplementary Information

### 2021-08-04 doc/manuscript/ForestGEO_treerings_SI.Rmd
replace LT composite plot excluding year with version including year

GLS_BCNM_legend = "Figure S10. Best GLS models including climate and DBH for BCNM"
GLS_SCBI_legend = "Figure S11. Best GLS models including climate and DBH for SCBI"
GLS_SCBI_year_legend = "Figure S12. Best GLS models including climate, DBH, and year for SCBI"
GLS_LT_legend = "Figure S13. Best GLS models including climate and DBH for LT"

@@

\newpage
## `r GLS_LT_legend`

![`r GLS_LT_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/NewMexico.png){ width=85% }

>>>>

GLS_BCNM_legend = "Figure S10. Best GLS models including climate and DBH for BCNM"
GLS_SCBI_legend = "Figure S11. Best GLS models including climate and DBH for SCBI"
GLS_SCBI_year_legend = "Figure S12. Best GLS models including climate, DBH, and year for SCBI"
GLS_LT_year_legend = "Figure S13. Best GLS models including climate, DBH, and year for LT"

@@

\newpage
## `r GLS_LT_year_legend`

![`r GLS_LT_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/NewMexico_with_Year.png){ width=85% }
